---
title: "OKC App"
author: "Daniel Mertus"
date: "11/18/2021"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, include=FALSE}
library(sqldf)
options(warn=-1)
```

```{r}
teamA_shots <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team A' ")
plot(teamA_shots[,2], teamA_shots[,3], main="Team A Shooting Dist", xlab="", ylab="")
teamA_C3 <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team A' and y <= 7.8 and (x >= 22 or x <= -22)")
points(teamA_C3[,2], teamA_C3[,3], col="red")
teamA_NC3 <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team A' and y > 7.8 and POWER(POWER(x,2) + POWER(y,2), 0.5) >= 23.75 ")
points(teamA_NC3[,2], teamA_NC3[,3], col="blue")
teamA_2PT <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team A' and ((y <= 7.8 and (x < 22 and x > -22)) or (y > 7.8 and POWER(POWER(x,2) + POWER(y,2), 0.5) < 23.75)) ")
points(teamA_2PT[,2], teamA_2PT[,3], col="green")

nrow(teamA_shots) 
nrow(teamA_C3) + nrow(teamA_NC3) + nrow(teamA_2PT)

```
\
`r (nrow(teamA_2PT)/nrow(teamA_shots)) * 100`% of Team A's shots were 2PTs, `r (nrow(teamA_C3)/nrow(teamA_shots)) * 100`% were C3s, and `r (nrow(teamA_NC3)/nrow(teamA_shots)) * 100`% were NC3s\
\
Team A had a eFG% of `r table(teamA_2PT$fgmade)[2] / nrow(teamA_2PT) * 100`% shooting 2PTs, `r (1.5 * table(teamA_C3$fgmade)[2]) / nrow(teamA_C3) * 100`% shooting C3s, and `r (1.5 * table(teamA_NC3$fgmade)[2]) / nrow(teamA_NC3) * 100`% shooting NC3s,\
```{r}
teamB_shots <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team B' ")
plot(teamB_shots[,2], teamB_shots[,3], main="Team B Shooting Dist", xlab="", ylab="")
teamB_C3 <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team B' and y <= 7.8 and (x >= 22 or x <= -22)")
points(teamB_C3[,2], teamB_C3[,3], col="red")
teamB_NC3 <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team B' and y > 7.8 and POWER(POWER(x,2) + POWER(y,2), 0.5) >= 23.75 ")
points(teamB_NC3[,2], teamB_NC3[,3], col="blue")
teamB_2PT <- read.csv.sql("./shots_data.csv", "select * from file where team = 'Team B' and ((y <= 7.8 and (x < 22 and x > -22)) or (y > 7.8 and POWER(POWER(x,2) + POWER(y,2), 0.5) < 23.75)) ")
points(teamB_2PT[,2], teamB_2PT[,3], col="green")

nrow(teamB_shots) 
nrow(teamB_C3) + nrow(teamB_NC3) + nrow(teamB_2PT)

```
\
`r (nrow(teamB_2PT)/nrow(teamB_shots)) * 100`% of Team B's shots were 2PTs, `r (nrow(teamB_C3)/nrow(teamB_shots)) * 100`% were C3s, and `r (nrow(teamB_NC3)/nrow(teamB_shots)) * 100`% were NC3s\
\
Team B had a eFG% of `r table(teamB_2PT$fgmade)[2] / nrow(teamB_2PT) * 100`% shooting 2PTs, `r (1.5 * table(teamB_C3$fgmade)[2]) / nrow(teamB_C3) * 100`% shooting C3s, and `r (1.5 * table(teamB_NC3$fgmade)[2]) / nrow(teamB_NC3) * 100`% shooting NC3s,\

